A review on Generative Learning in Computer Vision

### 2020-05-08 paper.tex
added InfoGAN

\subsubsection{Info GAN}

>>>>

\subsubsection{InfoGAN}
InfoGAN was proposed by Chen et al in 2016 \cite{b6}. InfoGAN is a GAN which utilises the information shared among a subset of the latent space. It also uses an unsupervised learning technique called disentagled representation which allocated different sets of dimensions by breaking down features of the data. Disentangled information represents a low representation of the data. With the introdcution of this technique, it makes the model to be truly unsupervised. InfoGAN as claimed by the authors contributes comparatively less computation cost when used with GAN also making it easier to train.
